Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-26 files/Chapter5/3D_FEM.tex
Chapter 3

For the this three-dimensional model, tri-cubix basis functions are used. These basis functions are an extension of the Hermite cubic basis functions from the two-dimensional model. Although this is more complex than using tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.

@@

Consider a set of $n$ linear independent three-dimensional scalar valued functions $\delta_i$. In this dissertation, these functions are tri-cubic basis functions (an extension of Hermite cubics from the two-dimensional model into three-dimensions). The functions $\delta_i$ satisfying the conditions of the test function space $T(\Omega)$ are called the admissible basis functions. Since there are a finite number if admissible basis functions, they can be numbered $\delta_1, \delta_2,...,\delta_k$.\\

>>>>

For the this three-dimensional model, piecewise Hermite tri-cubic basis functions are used. Although this is more complex than using piecwise tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.

@@

Consider a set of $n$ linear independent three-dimensional scalar valued functions $\delta_i$. In this dissertation, these functions are piecewise Hermite tri-cubic basis functions (an extension of Hermite cubics from the two-dimensional model into three-dimensions). The functions $\delta_i$ satisfying the conditions of the test function space $T(\Omega)$ are called the admissible basis functions. Since there are a finite number if admissible basis functions, they can be numbered $\delta_1, \delta_2,...,\delta_k$.\\
